Manuscript Preparation

### 2018-07-27 Houston/src/manuscript_preparation.Rmd
Modifications to manuscript_preparation.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain) # FIX: markovchain seems not compatible with R3.5.0
require(reshape)
require(survival)
require(caret)
require(e1071)
require(randomForest)
require(kernlab)
require(SuperLearner)
# knitr::opts_knit$set(root.dir = "~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/prepare_violation.R")
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/roll_over.R")
#knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

# confusion matrix and other performance metrics
fe.div2.performance <- confusionMatrix(data = fe.div2.result$pred, reference = fe.div2.result$severe, positive = "TRUE")
print(fe.div2.performance$table)
print(c(fe.div2.performance$overall["Accuracy"], fe.div2.performance$byClass[c("Sensitivity", "Specificity", "Precision", "F1")]))   
```

@@

pred.train <- predict(svm.model, labeled.data.lost.train)
mean(pred.train==labeled.data.lost.train$severe) # classification rate
```

@@

# separate predictors
x <- data.frame(labeled.data.lost.train[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
xtest <- data.frame(labeled.data.lost.result[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain) # FIX: markovchain seems not compatible with R3.5.0
require(reshape)
require(survival)
require(caret)
require(e1071)
require(randomForest)
require(kernlab)
require(SuperLearner)

## Abhishek Macbook
# knitr::opts_knit$set(root.dir = "~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/prepare_violation.R")
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/roll_over.R")

##Abhishek Desktop
knitr::opts_knit$set(root.dir = "D:/Github/CRIS/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
source("D:/Github/CRIS/violation-data-analysis/Houston/src/prepare_violation.R")
source("D:/Github/CRIS/violation-data-analysis/Houston/src/roll_over.R")

##Albert Macbook
# knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

# confusion matrix and other performance metrics
fe.div2.performance <- confusionMatrix(data = factor(fe.div2.result$pred), reference = factor(fe.div2.result$severe), positive = "TRUE")
print(fe.div2.performance$table)
print(c(fe.div2.performance$overall["Accuracy"], fe.div2.performance$byClass[c("Sensitivity", "Specificity", "Precision", "F1")]))   
```

@@

pred.train <- predict(svm.model, labeled.data.lost.train) # Returns value from 0 to 1. Needs to be thresholded to give 0 or 1
mean(pred.train==labeled.data.lost.train$severe) # classification rate
```

@@

# separate predictors
x <- data.frame(labeled.data.lost.train[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',

                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
xtest <- data.frame(labeled.data.lost.result[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
